%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[utf8]{inputenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    {\Huge \scshape Mohamed Wael ElTeir} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +20-1022740002 ~ \href{mailto:mohamedelteir@hotmail.com}{\raisebox{-0.2\height}\faEnvelope\ \nolinkurl{mohamedelteir@hotmail.com}} ~ 
    \href{https://linkedin.com/in/mohamedwelteir}{\raisebox{-0.2\height}\faLinkedin\ \nolinkurl{linkedin.com/in/mohamedwelteir}}  ~
    \href{https://github.com/MohamedWElteir}{\raisebox{-0.2\height}\faGithub\ \nolinkurl{github.com/MohamedWElteir}}
    \vspace{-8pt}
\end{center}

%----------SUMMARY----------
\section{Summary}
\resumeSubHeadingListStart
\item
  \small{
    {Skilled software engineer with a passion for building scalable applications and clean, efficient code. Proficient in the .NET framework and multiple programming languages, with strong problem-solving abilities and experience delivering high-quality projects. Driven to keep up with industry trends and modern development practices.} 
  }
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Alexandria University}{September 2021 -- May 2025}
      {Bachelor of Science in Computer Science}{GPA: 3.52}
    \resumeSubheading
      {Saint Marc College}{May 2007 -- August 2021}
      {Diploma}{GPA: 2.83}
  \resumeSubHeadingListEnd

%-----------Professional Training-----------
\section{Professional Training}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Coach Academy}{April 2024 -- October 2024}
      {Competitive Programming and Problem Solving}{}
      \resumeItemListStart
        \resumeItem{Participated in a 6-month training program focusing on competitive programming and problem-solving.}
        \resumeItem{Enhanced problem-solving skills and learned advanced algorithms and data structures.}
        \resumeItem{Achieved a 1100+ rating on Codeforces.}
      \resumeItemListEnd

      \resumeSubheading
        {Information Technology Institute (ITI)}{August 2024 -- September 2024}
        {Open Source Development track}{}
        \resumeItemListStart
          \resumeItem{Engaged in a 6-week training program centered on open-source development and software engineering principles.}
          \resumeItem{Developed a strong foundation in software engineering and open-source development.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd
  
%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}

        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Software Methodology
                \item Algorithms Analysis
                \item Database Management
                \item Artificial Intelligence
                \item Internet Technology
                \item Systems Programming
                \item Computer Architecture
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, Java, C++, GO, Python, JavaScript, TypeScript, Julia} \\
     \textbf{Technologies/Frameworks}{: ASP.NET, xUnit.NET, Jenkins, Jira, Docker, Git, GitHub, Postman} \\
     \textbf{Programming Concepts}{: Object Oriented Design and Programming, Data Structures, Algorithms } \\
     \textbf{Database Management Systems}{: MS SQL, MySQL} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

 
    \resumeSubheading
      {Upwork}{August 2019 -- March 2020}
      {Software Developer Freelancer}{Remote}
      \resumeItemListStart
        \resumeItem{Developed 5 websites for 2 clients that are being used till today.}
        \resumeItem{Assisted clients with enhancing their existing websites by integrating new features. Which resulted in a 20\% increase in user engagement.}
        \resumeItem{Explored ways to improve development and visual design using HTML, JavaScript, and CSS.}
      \resumeItemListEnd
  
  \resumeSubHeadingListEnd
\vspace{-16pt}
%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{University Grades Notifier API} $|$ \emph{.NET}}{June 2024}
          \resumeItemListStart
            \resumeItem{Engineered an API to authenticate with the university's portal, retrieve grade data, and dispatch push notifications upon the release of new grades.}
          \resumeItemListEnd
          \vspace{-13pt}
     \resumeProjectHeading
{\textbf{Mini Search Engine} $|$ \emph{Python} $|$ \faGithub \ \href{https://github.com/MohamedWElteir/Search-Engine-In-Python}{GitHub}}{April 2024}
\resumeItemListStart
\resumeItem{Created a basic search engine capable of processing and ranking documents based on relevance metrics such as Cosine-Similarity, Jaccard-Similarity, and others.}
\resumeItem{Enhanced the search engine's responsiveness and accuracy by implementing Likelihood Models, which improved the quality of search results by 2.5 times.}
\resumeItemListEnd
          \vspace{-13pt}
          \resumeProjectHeading
{\textbf{Turing Machine Simulator} $|$ \emph{C++} $|$ \faGithub \ \href{https://github.com/MohamedWElteir/Turing-Machine-Simulator}{GitHub}}{October 2023}
\resumeItemListStart
\resumeItem{Developed a console-based Turing Machine simulator for a Theory of Computation course, accurately emulating the behavior of a real Turing Machine. Written in C++, the simulator's performance was optimized by 30\% through the use of efficient algorithms.}
\resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------Achievements-----------
\section{Achievements}
  \resumeSubHeadingListStart
    \resumeSubheading
     {\textbf{Egyptian Collegiate Programming Contest (ECPC)} $|$ \href{https://icpc.global/ICPCID/8H1UPW16WJN6}{\faGlobe}}{2023, 2024} 
      {Contestant}{}
      \resumeItemListStart
        \resumeItem{Twice finalist in regional qualifications contests, solving a wide range of complex algorithmic challenges. With the highest rank of 53rd in the 2024 contest.}
      \resumeItemListEnd
    \resumeSubheading
    {\textbf{Meta Hacker Cup} $|$ \href{https://www.facebook.com/codingcompetitions/hacker-cup/2024/certificate/440863471706931}{\faGlobe}}{2024}
    {Contestant}{}
    \resumeItemListStart
    \resumeItem{Progressed to the first round of the competition, competing against the top 25,000 participants worldwide.}
    \resumeItemListEnd

    \resumeSubheading
    {IEEE AlexSB}{2024}
    {Contestant}{}
    \resumeItemListStart
    \resumeItem{Participated in the IEEE AlexSB Programming Contest, solving a series of algorithmic challenges in a timed environment.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------Volunteer Experience---------------
\section{Volunteer Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {HackerRank Campus Club,
AUFS}{January 2024 -- October 2024}
      {Head of the Backend track}{Alexandria University}
      \resumeItemListStart
        \resumeItem{Served as the head and instructor for the back-end track, utilizing the .NET framework to teach and mentor students.}
        \resumeItem{Led a highly productive team that successfully completed multiple projects and significantly improved post-campus performance.}
        \resumeItem{Managed the executive board of 5 members, conducting weekly meetings to monitor and drive progress in key areas.}
        \resumeItem{Directed a chapter of over 20 members, focusing on community service, teamwork, creativity, academic excellence, and mentorship.}
      \resumeItemListEnd
     
  \resumeSubHeadingListEnd
\end{document}
